---
title: "data.table"
author: "R'm Balım Peteğim"
date: "31 08 2020"
output: 
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_document:   
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

<style>
#TOC {
 color: 
 font-family: Calibri;
 background-color:
 border-color: darkred;
}
#header {
 color: darkred;
 font-family: Calibri;
 background-color:
}
body {
 font-family: Calibri;
 }
 
</style>

# Introduction to data.table Package

`data.table` package is used for the data manupilation processes. It is accepted as the fastest package for this purpose. Even if R is consired as bad for high volume data, this package makes all works faster than any other package. When it is compared with *dply* or *pandas* package of Python, it is the winner all the time. Also, most of other packages in R are built on data.table package.

```{r package}
pti <- c("data.table")
pti <- pti[!(pti %in% installed.packages())]
if(length(pti)>0){
    install.packages(pti)
}

library(data.table)
```

# Examples of data.table

## fread function
Also we can use `fread()` for reading the data from internet or local. This function works like `read.csv()` function but in a more efficient way.

```{r fread}
file <- if(file.exists("turkey_car_market.csv")) {
  "turkey_car_market.csv"
} else {
  url('https://raw.githubusercontent.com/pjournal/boun01g-data-mine-r-s/gh-pages/data.table/turkey_car_market.csv')
}
car_market = fread(file)
```

## data.table object

As other data manupilation packages, data.table has its own data type which is *data.table*. We can create an example data.table object like this:

```{r data.table object}
datatable = data.table(student_no = c(1, 2, 3, 4, 5),
                       names = c("A", "B", "C", "D", "E"),
                       city = c("Istanbul", "Adana", "Eskişehir", "Antalya", "Hakkari"))
datatable
```

We can use all functions in base R with data.table object like:

```{r base R}
nrow(car_market)
ncol(car_market)
summary(car_market)
str(car_market)
head(car_market)
```

## DT[i, j, by]

The most important consept of data.table package is the usage of data.table object. When we want to filter the data, we need to give that information in `i` parameter. If we want to select some of columns (or all of them), we need to use the `j` parameter. If we want to group the data with a column / columns, we need to indicate it in the `by` parameter.

### Filtering

For example, if we want to get all records whose prices(`Fiyat` column) are less than 50000 Turkish Liras, we can use this code:

```{r filtering}
car_market[Fiyat < 50000]
#car_market[car_market$Fiyat < 50000,] in base R
```

Also we can give more conditions with `&` or `|` operators.

```{r filtering2}
car_market[Fiyat < 50000 & Marka == 'Acura']
#car_market[car_market$Fiyat < 50000 & car_market$Marka == 'Acura',] in base R
```

If we want to get all rows except this condition we can use `!` sign.

```{r filtering3}
car_market[!(Fiyat < 50000 & Marka == 'Acura')]
```

### Selecting

For example, we need to get the head of the colours (`Renk` column). To do so, we can use these notations:

```{r selecting}
cols = c("Renk")
head(car_market[, Renk])
head(car_market[, .(Renk)])
head(car_market[, list(Renk)])
head(car_market[, c("Renk"), with = FALSE])
head(car_market[, 10, with = FALSE])
head(car_market[, cols, with = FALSE])
head(car_market[, ..cols])
```

We used the `with` argument. If we assign *FALSE* to that argument, it uses the character as the column name. `.()` and `list()` is used for selecting the columns.
As you can see, the first one returns a vector, not a data.table object. With that usage, we can not use data.table operations like:

```{r vector_selecting}
nrow(head(car_market[, Renk]))
```

We can select multiple columns with these usages:

```{r selecting2}
cols = c("Renk", "Fiyat")
head(car_market[, .(Renk, Fiyat)])
head(car_market[, list(Renk, Fiyat)])
head(car_market[, c("Renk", "Fiyat"), with = FALSE])
head(car_market[, c(10, 15), with = FALSE])
head(car_market[, cols, with = FALSE])
head(car_market[, ..cols])
```

We can select multiple rows with using slicing or excluding the columns with `!` sign. For example:

```{r selecting3}
head(car_market[, Marka:Fiyat])
head(car_market[, !c("Ä°lan Tarihi"), with = FALSE])
```

In selecting the columns we can use some operations like `%like%`. The usage of this operator is like this:

```{r selecting4}
car_market[, names(car_market) %like% 'Arac', with = FALSE]
```

We can rename the columns with `setnames` function like:

```{r rename}
setnames(car_market, c("Ä°lan Tarihi"), c("Date"))
setnames(car_market, c("Model YÄ±l", "YakÄ±t Turu"), c("Model_Year", "Fuel_Type"))
head(car_market)
```

We can sort the data with `setorder` function like:

```{r order asc}
head(setorder(car_market, Date))
```

It orders the data ascending by default. We can use `-` sign for descending and can order the data with multiple columns like:

```{r order desc}
head(setorder(car_market, Date, -Marka))
```

### Grouping

We can group the data with using the `by` parameter. We can get average prices for each brand like this:

```{r grouping}
car_market[, .(mean_price= mean(Fiyat)), by = Marka]
```

We can summarize the data for more than one column with respect to more than one column.

```{r grouping2}
car_market[, .(mean = mean(Fiyat), max = max(Fiyat)), by = c("Marka", "Arac Tip")]
```

We can get total number of rows with `.N` like:

```{r grouping3}
car_market[, .N, by = Marka]
```

## Index Operators

If we use the index of the data, we can perform better processes with respect to time. To set a column to the index we can use `setkey()` function like:

```{r setkey}
setkey(car_market, Date)
key(car_market)
head(car_market)
```

As you can see, the data is sorted after by key setting it. Alse we can give multiple index like:

```{r setkey2}
setkey(car_market, Date, Marka)
key(car_market)
```

We can group the data by the key(s) with `bykey` argument like:

```{r group bykey}
head(car_market[, .(mean_price= mean(Fiyat)), by = Date])
```

## Creating Columns

### Adding Columns

We can create columns in data.table package. To do so we need to use `:=` operator like:

```{r create}
head(car_market[, fpk := Fiyat / Km])
```

We can also create multiple columns.

```{r create2}
head(car_market[, c("kpf", "full_vehicle_type") := list(Km / Fiyat, paste(`Arac Tip Grubu`, `Arac Tip`))])
```

We can write sub queries like in SQL. We can show it from the code above:

```{r sub query}
car_market[, c("kpf", "full_vehicle_type") := list(Km / Fiyat, paste(`Arac Tip Grubu`, `Arac Tip`))][, .(kpf, full_vehicle_type)]
```

### Aggregation 

For the creation of new columns, we can use aggregate functions like min, max etc.

```{r aggregate}
car_market[, .(mean = mean(Fiyat, na.rm = TRUE),
median = median(Fiyat, na.rm = TRUE),
min = min(Fiyat, na.rm = TRUE),
max = max(Fiyat, na.rm = TRUE))]
```

We can summarize multiple columns like:

```{r aggregate2}
car_market[, .(mean(Fiyat), mean(Km))]
```

If we need to apply aggregation for more columns, we can use `.SD` and `.SDcols`. .SD means 'Subset of Data'. If we don't use .SDcols parameter, it includes all columns. If we use .SDcols, it applies that process for these columns.

```{r aggregate3}
car_market[, lapply(.SD, mean), .SDcols = c("Fiyat", "Km")]
```

Also, we can have multiple summarize function in the same line like:

```{r aggregate4}
car_market[, sapply(.SD, function(x) c(mean=mean(x), median=median(x)))]
```